### 2020-05-30 paper.tex
Conclusion

>>>>

We have talked to multiple people in order to understand how software engineers, and in particular frontend engineers, apply RP using RxJS for building applications. We have looked into how they debug their applications and could identify several struggles they have to overcome in this process. We could proof that the engineers inevitably tend to modify their source code once they do not understand how the RP runtime propagates values through its internal data-flow graph by observing professionals in an observational study.

On the way, we elaborated on previous, academical as well as non-academical efforts in the field of reactive debugging. We presented a selection of tools which leverage on their knowledge about the internal workings of RP runtime environments.

With \emph{UX}, \emph{Automatic Code Augmentation} and \emph{Integration} we finally proposed three concepts where we intend to improve on a software engineers debugging experience, hence answering our second research question RQ2. We plan to work further on these topics in an upcoming workshop paper within the scope of our master's studies research.
